Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-26 R0V0.tex
Minor updates

\begin{figure}
	\centering
%	\includegraphics[]{}
	%\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
	\caption{Illustration of the directed graphs representing the physical interaction between nodes $\mathscr{G}_p$, and the communication network $\mathscr{G}_c$. These may or may not be identical.}
	\label{fig:graph different illustration}
\end{figure}

@@

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for a fixed control $u$ for system~\eqref{eq:general system}, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t),\Delta(t))\leq -\lambda V(X(t),\Delta(t))
 	 	 \end{equation}
 	 	 holds, where $X(t):=X(t,x,u)$ and $\Delta(t):=\Delta(t,x,\delta_x,u,0)$, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\to\mathbb{R}^{n\times m}$.

@@

\mypara Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every pair of solutions $X(\cdot,x,u)$ and $X^\ast(\cdot,x^\ast,u^\ast)\in\mathbb{R}^n$, and at each time instant $t\geq0$,  there exist a smooth geodesic curve $\gamma:\{t\}\times [0,1]\to\mathbb{R}^n$ connecting them. Then the differential feedback law $K(x)$ can be integrated along $\gamma$:
\begin{equation}\label{eq:contracting feedback law}
	k(x,=u^\ast(t)+\int_0^1 K(\gamma(t,s))\gamma_s(t,s)\,ds\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive. Further conditions are discussed in \cite{manchester_existence_2018}.

>>>>

\begin{figure}
	\centering
%	\includegraphics[]{}
	%\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
	\includegraphics[width=\columnwidth]{./imgs/physical_network_graphs}
	\caption{Illustration of the directed graphs representing the physical interaction between nodes $\mathscr{G}_p$, and the communication network $\mathscr{G}_c$. These may or may not be identical.}
	\label{fig:graph different illustration}
\end{figure}

@@

\begin{definition}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for a fixed control $u$ for system~\eqref{eq:general system}, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t),\Delta(t))\leq -\lambda V(X(t),\Delta(t))
 	 	 \end{equation}
 	 	 holds, where $X(t):=X(t,x,u)$ and $\Delta(t):=\Delta(t,x,\delta_x,u,0)$, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

\begin{definition}[{\cite{Manchester2014a}}]
	A metric for system \eqref{eq:general system} is said to be a \emph{control contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\to\mathbb{R}^{n\times m}$.

@@

\mypara Step 2 (Online controller integration). The feedback law for system \eqref{eq:general system} can be obtained by integration as follows. Let $u^\ast:\mathbb{R}_{\geq0}\to\mathbb{R}^m$ be a control for system \eqref{eq:general system}, from Hopf-Rinow theorem (cf. \cite[Theorem 7.7]{Boothby1986}), for every pair of solutions $X(\cdot,x,u)$ and $X^\ast(\cdot,x^\ast,u^\ast)\in\mathbb{R}^n$, and at each time instant $t\geq0$,  there exist a smooth geodesic curve $\gamma:\{t\}\times [0,1]\to\mathbb{R}^n$ connecting them. Then the differential feedback law $K(x)$ can be integrated along $\gamma$:
\begin{equation}\label{eq:contracting feedback law}
	k(t)=u^\ast(t)+\int_0^1 K(\gamma(t,s))\gamma_s(t,s)\,ds\;,
\end{equation}
where $s\in[0,1]$, is a feedback law rendering any forward complete solution $X^\ast$ to system~\eqref{eq:general system} globally exponentially stable.

@@

\mypara For linear time-invariant systems with the property that solutions starting in the positive orthant remain in the positive orthant (also known as positive systems), the stability of the origin is equivalent to the existence of a quadratic Lyapunov function described by a matrix $P=P^\top\succ0$ with diagonal structure \cite{berman_nonnegative_1994}. Thus, locally (around the origin) the assumption of a diagonal structure is not restrictive.
